---
title: "Getting Started with plssemtools"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with plssemtools}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", eval = FALSE)
```

## 1. Define your model

Every analysis starts with a small YAML file describing your constructs,
their items, and the hypothesized structural paths between them:

```yaml
constructs:
  Psychological Factors:
    type: reflective
    items: [PS_1, PS_2, PS_3]
  Social Factors:
    type: reflective
    items: [SO_1, SO_2, SO_3, SO_4]
  Environmental Factors:
    type: reflective
    items: [EN_1, EN_2, EN_3]
  Good Shopping Vibes:
    type: reflective
    items: [GV_1, GV_2, GV_3, GV_4, GV_5]

paths:
  - from: [Psychological Factors, Social Factors, Environmental Factors]
    to: Good Shopping Vibes
```

Save this as `model_spec.yml`. You never need to write `seminr::constructs()`
or `seminr::relationships()` calls by hand again -- `load_model_spec()` builds
them for you and validates that every item referenced actually exists.

## 2. Run the full pipeline

```{r}
library(plssemtools)

result <- run_pls_pipeline(
  data       = "your_survey_data.csv",
  spec       = "model_spec.yml",
  output_dir = "pls_output",
  nboot      = 5000,
  seed       = 1234
)
```

This single call:

1. Loads and validates your CSV against the model spec (catches missing/typo'd columns immediately)
2. Computes construct- and item-level descriptive statistics
3. Estimates the PLS-SEM model
4. Computes reliability/validity diagnostics (Cronbach's alpha, CR, AVE, Fornell-Larcker, HTMT, VIF, cross-loadings)
5. Computes Q-squared via k-fold prediction
6. Runs bootstrapped resampling for path significance
7. Generates all eight publication-quality figures in PNG and PDF

## 3. Inspect results programmatically

```{r}
result$model_summary$reliability
result$construct_descriptives
result$q2_table
```

## 4. Reuse on a new dataset

Copy your YAML file, point it at new column names, and re-run. Nothing in
the package needs to change -- that's the entire point.

## 5. Customize a single figure

```{r}
th <- plssem_theme(base_family = "serif", base_size = 12)
p <- plot_path_diagram(result$model_summary, result$spec,
                        boot_summary = result$boot$summary, theme = th)
ggplot2::ggsave("figure1.pdf", p, width = 8, height = 5, device = grDevices::cairo_pdf)
```
